
significant changes 

employ benefits from excel and fitness tracking apps.
what is the benefit of excel?
what is disadvantages?
these disadvantages can be solved with fitness tracking app. 

1. new features implementation (Tag & Muscle & Workout Analysis)

% Section - Muscle visualisation

% section - tag


// how does it trigers filtering

[ live data ]
[ TagAdapter ]


% section - analysis 
\model
tag storage
save tags when it's added
delete and edit tag work

% Status Fragment 
will change the status layout
implementing the graph
status card
status recycler
table setup object
grapg visibility

% screenshot 
- > today's log - match parent
the use of an empty row at the end of each session improves visual separation and helps distinguish between sessions.
when add log or card, the most current one to the first index
I will do the add log activity first
add log layout
one rep max with two decimal with kg
one rep max bar
make part bold
new line instead of coloum
implementing the graph
today box : user don't know where to log
table setup object
add log activity keep updating thr logs
grapg visibility
1rm bar visibility
1rm visibility and formatting, muscle text formattin
floating button loaction


log 
status

\predicted 1RM
update existing data structure (added 1RM)
deal with empty list for algorithm
One rep max -> 1rm

data structure update


% section - Setting Fragment 

screenshots 
emails receieved

(3) storage sequence adoptation 
    ExerciseCard, ExerciseLog






\\\version 1.5 : 
research on muscle group and visualisation
didn't have 1rm for log, card
delete [
    and analysis available on the logging screen. 
this is the noticable unique feature of this app. 
other exercise apps are separating the analysis screen and the logging screen, 
also, not only giving the past logs, can see the progress at a glance. 
so it is also better than just using excel which simply gives you past logs.
Making analysis is possible with excel as well, but for this, users need to manually setup all the things for each exercise they add.
but with this app, 
]


(3) version 2.1 implementation - app deployment (app store release, gitHub release)
focus on researched factors (user centered app)
enhancing user experiences
(minimalise steps that user needs to take to log their progress, user can customise set recording, long click to delete a card with warning)

market introduction

package domain changed
debuggable
turn off debugging
version name update
app version


conclusion of version 2 implementation

Status fragment is designed to combine the benefit of excel and fitness tracking app.
giving all tje exercies' analysis on one single screen, user can take the benefit of excel which enable people to see all the datas on one screen,
which makes people easily compare their data and see them at a glance.
But also, this gives you the benefit of fitness tracking app.
This includes that
1. user can simply enter their records and don't need to do anything else to see the data and analysis.
2. user can easily filter the exercies they want to see the analysis or logs with the groups they customised.
this is a unique feature provided only on this app which enable user to be able to check the analysis and data on one screen.
By this feature, user don't need to go through and enter each exercise analysis and log to check or compare them.
This solves the reason why people don't use fitness tracking app and use excel instead providing the benefit of excel but also provide even more advantages.
asked people who used the excel instead of fitness app
they said it is indeed helpful and useful feature
and it is even better than excel
as it makes them easily manage the data and it also provide analysis and filter the data.

analysis is available on the logging screen as well.
this is the noticable unique feature of this app. 
other exercise apps are separating the analysis screen and the logging screen, 
also, not only giving the past logs, can see the progress at a glance. 
so it is also better than just using excel which simply gives you past logs.
Making analysis is possible with excel as well, but for this, users need to manually setup all the things for each exercise they add.

feedback agaile reflection


version 3 dissertation

survey result
user feedbacks -> solution


git log categorising
functionality - why did I implement it / how did I implement it?
app scalability / technical explanation



critical evaluation
user feedback
what can I do better
following studies

4. Evaluate the app in terms of efficiency and user satisfaction and demonstrate that the proposed enhancements are beneficial.
	smart goal evaluation
	app reviews
	what I can do better if I do it again next time?